---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---
```{r, echo=FALSE}
require(plyr)
```

## Loading and preprocessing the data
```{r}
activity = read.csv("activity/activity.csv")
activity_complete = activity[complete.cases(activity),]
```

## What is mean total number of steps taken per day?
```{r}
steps_per_day = ddply(activity_complete, c("date"), summarize, total_steps = sum(steps))
hist(steps_per_day$total_steps, main = "Histogram of steps taken per day", xlab = "Total steps per day")
avg_steps_per_day = mean(steps_per_day$total_steps)
rounded_avg_steps_per_day = round(avg_steps_per_day, 0)
median_steps_per_day = median(steps_per_day$total_steps)
```
Average total number of steps taken per day is `r rounded_avg_steps_per_day`.
The median is `r median_steps_per_day` steps.

## What is the average daily activity pattern?
```{r}
steps_per_interval = ddply(activity_complete, c("interval"), summarize, avg_steps = mean(steps))
with(steps_per_interval, plot(interval, avg_steps, type = "l"))
max_steps_per_interval = steps_per_interval[which.max(steps_per_interval$avg_steps), ]
```

The most steps (```r max_steps_per_interval$avg_steps```) were taken at interval ```r max_steps_per_interval$interval```

## Imputing missing values
```{r}
count_of_missing_data = nrow(activity) - nrow(activity_complete)
avg_steps_per_day = ddply(activity_complete, c("date"), summarize, avg_steps = mean(steps))
merged_activity_with_avg = merge(activity, avg_steps_per_day, by = "date", all.x = TRUE)
# put zeroes in place on NA avg per day:
merged_activity_with_avg$avg_steps[is.na(merged_activity_with_avg$avg_steps)] <- 0
# and now use avg per day as the steps in interval
merged_activity_with_avg$steps[is.na(merged_activity_with_avg$steps)] <- merged_activity_with_avg$avg_steps[is.na(merged_activity_with_avg$steps)]
activity_with_avg = merged_activity_with_avg[,c("steps", "date", "interval")]

steps_per_day = ddply(activity_with_avg, c("date"), summarize, total_steps = sum(steps))
hist(steps_per_day$total_steps, main = "Histogram of steps taken per day", xlab = "Total steps per day")
avg_steps_per_day = mean(steps_per_day$total_steps)
rounded_avg_steps_per_day = round(avg_steps_per_day, 0)
median_steps_per_day = median(steps_per_day$total_steps)

```
There are ```r count_of_missing_data``` rows that are missing original data.
After filling in NAs with zeroes (it turns out that all of the NAs apply to complete days), the new average total number of steps taken per day is `r rounded_avg_steps_per_day`.
The median is `r median_steps_per_day` steps.

It basically treats a day without any log as a day with 0 steps taken. Because of this, both the average and the median dropped. But it is unreasonable to assume that missing days are equivalent to days with zero steps. A different approach might be considered (take an average from day before and day after) - however this average would not work for weekends for instance.

## Are there differences in activity patterns between weekdays and weekends?
